Towards a Machine Learning approach for Aggregate Computing

### 2021-07-20 paper-2021-woa-ac-ml.tex
cps to cas
more on introduction

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
\todo[inline, color=red]{max pages : 16}
\section{Introduction}
Aggregate Computing~\cite{DBLP:journals/computer/BealPV15}
\todo[inline]{walkthrogh Cyber Physical Systems, why they are hard}
\todo[inline]{Brief description of declarative approaches, pros and cons}
\todo[inline]{Brief description of machine learning approaches (MARL and GNN for communication), pros and cons}
\todo[inline]{Declare our direction: Combination to declarative and automatic approach}
\todo[inline]{Outline}

\section{Background and Related Work}
\todo[inline]{walkthrogh traditional engineering way to design CPS}
\todo[inline]{walkthrogh Aggregate Computing}
\todo[inline]{walkthrogh Machine learning approach applied in MARL}
\todo[inline]{current limitation (application specific, not large scale, centralised in some cases,..)}
\todo[inline]{novel work on GNN -- agent learn to communicate -- node size indipendent~\cite{DBLP:conf/corl/TolstayaGPP0R19}}

>>>>

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
\todo[inline, color=red]{max pages : 16}
\section{Introduction}
Aggregate Computing~\cite{DBLP:journals/computer/BealPV15}
\todo[inline]{walkthrogh CAS, why they are hard}
Nowadays, computer engineers have to deal with Collective Adaptive Systems (CASs) due to the increasing interconnected computational devices placed in ever-changing environments.
 Examples of those include robot swarm, smart cities and augmenting crowds.
A CAS is characterised by 
\begin{itemize}
\item a global order that emerges from local node interactions, 
\item  decentralised control, and 
\item adaptive behaviours towards environmental changes to pursuit a collective goal.
\end{itemize}
CAS are notoriously hard to design due as part of complex systems. 
%
So, over the years, in literature, various approaches aim at handling this complexity. 
%
Some of them take inspiration from the natural system composed of social animals -- like bees, fish and ants. 
%
Here, a sort of hive mind arises -- something referred to as swarm intelligence -- born from local interactions between agents. 
%
This kind of behaviour is called self-organisation, namely a global order that emerges from continuous interactions between simple entities.

Initially, researchers try to bring those properties in the computer science world by miming the collective behaviour bottom-up, 
 namely trying to find the single node behaviour to reach a global behaviour, e.g. flocking, foraging, etc.
%
Though, this mapping isn't easily definable -- since we handle complex systems -- therefore novel techniques move the design focus by the ensemble level,
 specifying the system behaviour as a whole.

\todo[inline]{Brief description of declarative approaches, pros and cons}
\todo[inline]{Brief description of machine learning approaches (MARL and GNN for communication), pros and cons}
\todo[inline]{Declare our direction: Combination to declarative and automatic approach}
\todo[inline]{Outline}

\section{Background and Related Work}
\todo[inline]{walkthrogh traditional engineering way to design CAS}
\todo[inline]{walkthrogh Aggregate Computing}
\todo[inline]{walkthrogh Machine learning approach applied in MARL}
\todo[inline]{current limitation (application specific, not large scale, centralised in some cases,..)}
\todo[inline]{novel work on GNN -- agent learn to communicate -- node size indipendent~\cite{DBLP:conf/corl/TolstayaGPP0R19}}
